---
title: "Calendly"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

## Preview

```{r, echo = FALSE, hide = TRUE}
root_dir <- rprojroot::find_root(rprojroot::has_dir(".git"))
yaml <- yaml::read_yaml(file.path(root_dir, "_config_automation.yml"))

## For github
calendly <- readr::read_tsv(file.path("metricminer_data", "calendly", "calendly.tsv"))

## For google 
# calendly <- googlesheets4::read_sheet(yaml$calendly_googlesheet)
```

```{r}
knitr::kable(calendly)
```

## Setting Up Calendly

1. To set up calendly authorization [go here](https://calendly.com/integrations/api_webhooks) and click "Generate Token".
2. Underneath "Choose a name for this token" pick a name that will remind you of this project.
3. Click "Create Token" and it will send you an authorization code to your email.
4. Click "Copy Token" and keep this handy.
5. Return to your metricminer dashboard repository and go to `Settings` > `Secrets and variables` > `Actions`.
6. Click on `New repository secret`. Name your new secret *exactly* `METRICMINER_CALENDLY`
7. Paste your token into the `Secret` box and then click the green "Add secret" button.

After you've set up authorization you'll need to check the following items in the `_config_automation.yml` file.

- [ ] In the `config_automation.yml` file, make sure that `refresh-calendly` is set to "yes".
- [ ] Optionally, if you are saving data to google, specify a googlesheet ID you'd like the CRAN data to be saved to. This will only be relevant if you've set `data_dest` to `google`.
```
###### Calendly ######
refresh-calendly: yes
calendly_googlesheet:
```

## Customizing the data 

In order to customize the data you are downloading from calendly you can modify the 
`refresh-scripts/refresh-calendly.R` script in your repository. 

You can take a look at the [`metricminer` R package documentation](https://hutchdatascience.org/metricminer/articles/getting-started.html) for more details about the functions and what is possible. 

If you have a metric need that is not currently fulfilled by `metricminer` or `metricminer-dashboard` we encourage you to [file a GitHub issue with us and let us know about your new feature idea (or bug report)](https://github.com/fhdsl/metricminer/issues/new/choose). 

