---
title: "CRAN"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

## Preview

```{r, echo = FALSE, hide = TRUE, message = FALSE}
library(tidyverse)

root_dir <- rprojroot::find_root(rprojroot::has_dir(".git"))
yaml <- yaml::read_yaml(file.path(root_dir, "_config_automation.yml"))

## For github
cran <- readr::read_tsv(file.path("metricminer_data", "cran", "cran.tsv"))

## For google
# cran <- googlesheets4::read_sheet(yaml$cran_googlesheet)
```

Total CRAN downloads for all packages: 

```{r}
cran %>% dplyr::summarize(download_total = sum(count))
```
CRAN package downloads over time, summarized by month. 

```{r, message = FALSE}
cran_stats <- cran %>%
  separate(date, into=c("year", "month name", "day"), sep = "-") %>%
  unite("Month", c("year", "month name"), sep='-', remove=TRUE) %>%  
  group_by(Month, package) %>%
  summarise(monthly_downloads = sum(count)) %>% #summarize monthly downloads by package
  filter(monthly_downloads > 0) #drop the 0's

ggplot(cran_stats, aes(Month, monthly_downloads, group=package, color = package)) +
  geom_line() +
  geom_point() +
  theme(panel.background = element_blank(), panel.grid = element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x = NULL,
       y = "Monthly Downloads",
       color = "R Packages")
```

## Setting up CRAN

In the `_config_automation.yml` you will need to specify a few things.

```
###### CRAN ######
refresh-cran: yes
cran_packages: [ metricminer, ottrpal ]
cran_googlesheet:
```

- [ ] In the `config_automation.yml` file, make sure that `refresh-cran` is set to "yes".
- [ ] In the `cran_packages` of your `config_automation.yml`, type the names of the packages that you'd like to collect data from on CRAN. Type them exactly as they are spelled, case sensitive, separated by commas. Delete the example package names we've put there.
- [ ] Optionally, if you are saving data to google, specify a googlesheet ID in `cran_googlesheet` you'd like the CRAN data to be saved to. This will only be relevant if you've set `data_dest` to `google`.
