---
title: "Google Analytics"
output: 
  html_document:
  toc: true
  toc_float: true
  toc_collapsed: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

## Setting up Google Analytics

## Preview

```{r, echo = FALSE, hide = TRUE, message = FALSE}
root_dir <- rprojroot::find_root(rprojroot::has_dir(".git"))
yaml <- yaml::read_yaml(file.path(root_dir, "_config_automation.yml"))

## For google analytics
ga_metrics <- readr::read_tsv(file.path("metricminer_data", "ga", "ga_metrics.tsv"))
ga_dimensions <- readr::read_tsv(file.path("metricminer_data", "ga", "ga_dimensions.tsv"))
ga_link_clicks <- readr::read_tsv(file.path("metricminer_data", "ga", "ga_link_clicks.tsv"))


## For google 
# ga_metrics <- googlesheets4::read_sheet(yaml$ga_googlesheet, sheet = "metrics")
# ga_dimensions <- googlesheets4::read_sheet(yaml$ga_googlesheet, sheet = "dimensions")
# ga_link_clicks <- googlesheets4::read_sheet(yaml$ga_googlesheet, sheet = "link_clicks")
```

```{r}
knitr::kable(ga_metrics)
```


```{r}
knitr::kable(ga_dimensions)
```


```{r}
knitr::kable(ga_link_clicks)
```

### Setting up Google Analytics

[Follow the steps from the above section to authenticate Google](#setting-up-google-authentication) -- make sure that the account you have authenticated for has access to the Google Analytics properties you wish to collect.

We'll need to collect the Google Analytics property IDs for the websites you want to retrieve data from.

1. Go to https://analytics.google.com/ -- You may have to login. These instructions are assuming you have already set up Google Analytics and have been collecting data.
2. Then click on the website at the top of the navbar. It will bring you to a dropdown that shows all your websites.

<img src = "resources/images/google-analytics-dropdown.png" width = "50%">

4 .Click on one of the websites where you'd like to retrieve data from. The URL will look something like this:
```
https://analytics.google.com/analytics/web/?authuser=1#/p<PROPERTY_ID_HERE>/reports/home
```
5. Copy the property id and put it in the `ga_property_ids:` part of the `_config_automation.yml`.

Repeat these same steps for all the properties you'd like to collect data for, separating the IDs by commas. Delete the example IDs we have put there as placeholders.

```
###### Google Analytics ######
refresh-ga: yes
ga_property_ids: [ 422671031, 422558989 ]
ga_googlesheet:
```

- [ ] In the `config_automation.yml` file, make sure that `refresh-ga` is set to "yes".
- [ ] Optionally, if you are saving data to Google, specify a googlesheet ID in `ga_googlesheet` you'd like the GitHub data to be saved to. This will only be relevant if you've set `data_dest` to `google`.
