---
title: "YouTube"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

## Preview

```{r, echo = FALSE, hide = TRUE, message = FALSE, warning = FALSE}
root_dir <- rprojroot::find_root(rprojroot::has_dir(".git"))
yaml <- yaml::read_yaml(file.path(root_dir, "_config_automation.yml"))

## For Youtube
youtube <- readr::read_tsv(file.path("metricminer_data", "youtube", "youtube.tsv"))

## For youtube
```

## Data information

- `viewCount` how many times has the video been viewed?
- `likeCount` how many times has the video been liked?
- `dislikeCount` - how many times has the video been disliked?
- `favoriteCount` - how many times has the video been favorited?
- `commentCount` - how many comments on the video?

```{r}
knitr::kable(youtube)
```

## Setting up YouTube

[Follow the steps from the above section to authenticate Google](#setting-up-google-authentication) -- make sure that the account you have authenticated for has access to the YouTube you wish to collect.

Go to a video you'd like to collect data from. The URL should look something like this:
```
https://www.youtube.com/watch?v=<YOUTUBE_VIDEO_ID_HERE>
```
Extract the Youtube Video ID from the URL and put it in the `video_ids` section of the `_config_automation.yml` file. Delete the example IDs we have put there as placeholders.
Do this for each video you'd like to collect data from and separate the IDs with commas.

```
###### YouTube ######
refresh-youtube: yes
video_ids: [ XN_QPRrJZAw, YkYnni-WuaQ ]
youtube_googlesheet:
```

- [ ] In the `_config_automation.yml` file, make sure that `refresh-slido` is set to "yes".
- [ ] Optionally, if you are saving data to Google, specify a googlesheet ID in `youtube_googlesheet` that you'd like the GitHub data to be saved to. This will only be relevant if you've set `data_dest` to `google`.

## Customizing the YouTube Data

In order to customize the data you are downloading from your YouTube you can modify the
`refresh-scripts/refresh-youtube.R` script in your repository.

You can take a look at the [`metricminer` R package documentation](https://hutchdatascience.org/metricminer/articles/getting-started.html) for more details about the functions and what is possible.

If you have a metric need that is not currently fulfilled by `metricminer` or `metricminer-dashboard` we encourage you to [file a GitHub issue with us and let us know about your new feature idea (or bug report)](https://github.com/fhdsl/metricminer/issues/new/choose).
