---
title: "YouTube"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

## Preview

```{r, echo = FALSE, hide = TRUE}
root_dir <- rprojroot::find_root(rprojroot::has_dir(".git"))
yaml <- yaml::read_yaml(file.path(root_dir, "_config_automation.yml"))

## For Youtube
youtube <- readr::read_tsv(file.path("metricminer_data", "youtube", "youtube.tsv"))

## For youtube
```

```{r}
knitr::kable(youtube)
```

### Setting up YouTube

[Follow the steps from the above section to authenticate Google](#setting-up-google-authentication) -- make sure that the account you have authenticated for has access to the YouTube you wish to collect.

Go to a video you'd like to collect data from. The URL should look something like this:
```
https://www.youtube.com/watch?v=<YOUTUBE_VIDEO_ID_HERE>
```
Extract the Youtube Video ID from the URL and put it in the `video_ids` section of the `_config_automation.yml` file. Delete the example IDs we have put there as placeholders.
Do this for each video you'd like to collect data from and separate the IDs with commas.

```
###### YouTube ######
refresh-youtube: yes
video_ids: [ XN_QPRrJZAw, YkYnni-WuaQ ]
youtube_googlesheet:
```

- [ ] In the `config_automation.yml` file, make sure that `refresh-slido` is set to "yes".
- [ ] Optionally, if you are saving data to Google, specify a googlesheet ID in `youtube_googlesheet` that you'd like the GitHub data to be saved to. This will only be relevant if you've set `data_dest` to `google`.
